Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-29 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Don't add performance metrics to colData before plotting nrejects by bins

**Still to-do: consider multiple covariates for methods that allow this.**

@@

head(assay(sb))
head(colData(sb))
sb@performanceMetrics[[1]]

# estimate perf metrics 
sb <- estimatePerformanceMetrics(sb, alpha=seq(0.01, 0.10, 0.01), addColData=TRUE)
```

>>>>

**Still to-do: repeat for additional covariate (MAF).**

@@

head(assay(sb))
head(colData(sb))
sb@performanceMetrics[[1]]
```
